Incentivizing Exploration with Unbiased History

### 2018-11-02 intro.tex
Stopping for the night, I think.

We take a step back and re-examine these assumptions. We ask: How would users interpret messages/recommendations generated by a disclosure policy? More importantly, how to design disclosure policies that would be interpreted by users in a predictable way, while ensuring good exploration-exploitation balance? Which conceptual framework should we use to reason about the user response to a disclosure policy, in the absence of the standard assumptions?

Consider the \emph{full-disclosure policy} that always reveals all information available to the principal. We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it. However, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}.

>>>>

We take a step back and re-examine these assumptions. We ask: How would users interpret messages/recommendations generated by a disclosure policy? More importantly, how to design disclosure policies that would be interpreted by users in a predictable way, while ensuring good exploration-exploitation balance? Without the standard assumptions, which conceptual frameworks can be used to reason about the user response to a disclosure policy in precise terms?

We build one such conceptual framework for a particular type of disclosure policies. Consider the \emph{full-disclosure policy} that reveals the full history of observations from the previous users. We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it. Unfortunately, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}. However, for the sake of the argument, what if the policy reveals the history for every other agent, rather than the history for all agents? We posit that users would trust such policy, too. Given a large volume of data, we posit that users would not be too unhappy with having access to only a fraction this data. A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user is chosen in advance, without looking at the observations. In particular, the disclosure policy cannot subsample the observations that make a particular action look good.

\ascomment{stopped for the day ...}
